### 2015-02-27 fundamentals/examples.tex
double period
then->than
some edits

The success of the \Cyclus simulator can be measured in many ways.  The most
compelling are demonstrations of fundamental simulation capability and of the
feasibility of the \Cyclus community-driven development model. Nascent promising
growth of the \Cyclus ecosystem at multiple institutions indicates that a fuel
cycle simulator can advance in this community-driven development
paradigm. Additionally, simulation results for both once-through and more
complex recycling scenarios demonstrate that \Cyclus possesses the fundamental
fuel cycle simulation capabilities to contribute to the field.

@@

The \Cyclus community-driven software development model seeks to break the
unproductive proliferation of overspecialized simulators. It instead leverages
the collective expertise of fuel cycle researchers toward a single, more
extensible, tool. Through the targeted
contributions of those researchers, an ecosystem of capabilities should emerge.
The \Cyclus `Ecosystem' is the collection of tools, calculation libraries,
archetypes, data, and input files intended for use with the \Cyclus simulator.
Members of the ecosystem include:
\begin{itemize}
\item the archetypes provided in the \Cycamore \cite{carlsen_cycamore_2014}
repository
\item the archetypes created by researchers
\item isotopic composition data
\item historical facility deployment data
\item the \Cyclus \gls{GUI} tool Cyclist
\item fundamental analysis tools in the \Cyclus toolkit
\item tools for \Cyclus optimization, parallelization, and development
\end{itemize}
Taken together, these form an ecosystem of capabilities. Over time, this
ecosystem will grow as archetype developers, kernel developers, and
even users contribute capabilities developed for their own needs. Indeed, the
long-term vision for the \Cyclus framework predicts an ever-expanding ecosystem
of both general and specialized capability extensions.

@@

    \item \textbf{Reactor} (\Class{cycamore::Reactor}): This is a reactor
        model that requests any number of input fuel types and transmutes them
        to static compositions when they are burnt and discharged from the
        core.  . The reactor was configured to model a light water reactor
        with a 3 batch core (20,000 kg HM per batch) operating on an 18 month
        cycle with a 2 month refuel time.  The reactor was also configured to
        take in either enriched \gls{UOX} fuel or recycled \gls{MOX} fuel.

@@

Modifying the input file specification to model each of the 3 fuel cycles was
done by making simple adjustments to the commodities and trade preferences for
each of the facilities.  The reactor was configured to request recycled \gls{MOX}
fuel with a higher preference then new \gls{UOX} fuel. For the once through case,
the \Class{Reactor} was set to offer all spent fuel as waste.  For the 1-pass
recycle case, the \Class{Reactor} offered spent \gls{UOX} into a spent fuel market,
but spent \gls{MOX} is still offered as waste.  In the infinite-pass recycle case,
the \Class{Reactor} offers all burned fuel into a spent fuel market. The
separations facility requests spent fuel with a higher preference than the
repository resulting in preferential recycle.  All these preferences are easy
to adjust and \Cyclus dynamically handles supply constraints and non-uniform
preference resolution.  It is notable that separations and recycle fuel
fabrication capacity are deployed identically in all simulations.  In the once
through case, the recycling loop never acquires material, and so reactors
always receive fresh \gls{UOX} fuel.  The \gls{DRE} ensures everything operates
smoothly in all cases.

>>>>

The success of the \Cyclus simulator can be measured in many ways.  The most
compelling are demonstrations of fundamental simulation capability and of the
feasibility of the \Cyclus community-driven development model. Promising
growth of the \Cyclus ecosystem at multiple institutions indicates that a fuel
cycle simulator can advance in this community-driven development
paradigm. Additionally, simulation results for both once-through and more
complex recycling scenarios demonstrate that \Cyclus possesses the fundamental
fuel cycle simulation capabilities to contribute to the field.

@@

The \Cyclus community-driven software development model seeks to break the
proliferation of specialized simulators. It instead leverages
the collective expertise of fuel cycle researchers toward a single, more
extensible, tool. Through the targeted
contributions of those researchers, an ecosystem of capabilities should emerge.
The \Cyclus `Ecosystem' is the collection of tools, calculation libraries,
archetypes, data, and input files intended for use with the \Cyclus simulator.
Members of the ecosystem include:
\begin{itemize}
\item the archetypes provided in the \Cycamore \cite{carlsen_cycamore_2014}
repository
\item the archetypes created by researchers
\item isotopic composition data
\item historical facility deployment data
\item the \Cyclus \gls{GUI} tool Cyclist
\item fundamental analysis tools in the \Cyclus toolkit
\item tools for \Cyclus optimization, parallelization, and development
\end{itemize}
Taken together, these form an ecosystem of capabilities. Over time, this
ecosystem will grow as archetype developers, kernel developers, and
even users contribute capabilities developed for their own needs. Indeed, the
long-term vision for the \Cyclus framework predicts an ever-expanding ecosystem
of both general and specialized capability extensions.

@@

    \item \textbf{Reactor} (\Class{cycamore::Reactor}): This is a reactor
        model that requests any number of input fuel types and transmutes them
        to static compositions when they are burnt and discharged from the
        core. The reactor was configured to model a light water reactor
        with a 3 batch core (20,000 kg HM per batch) operating on an 18 month
        cycle with a 2 month refuel time.  The reactor was also configured to
        take in either enriched \gls{UOX} fuel or recycled \gls{MOX} fuel.

@@

Modifying the input file specification to model each of the 3 fuel cycles was
done by making simple adjustments to the commodities and trade preferences for
each of the facilities.  The reactor was configured to request recycled \gls{MOX}
fuel with a higher preference than new \gls{UOX} fuel. For the once through case,
the \Class{Reactor} was set to offer all spent fuel as waste.  For the 1-pass
recycle case, the \Class{Reactor} offered spent \gls{UOX} into a spent fuel market,
but spent \gls{MOX} is still offered as waste.  In the infinite-pass recycle case,
the \Class{Reactor} offers all burned fuel into a spent fuel market. The
separations facility requests spent fuel with a higher preference than the
repository resulting in preferential recycle.  All these preferences are easy
to adjust and \Cyclus dynamically handles supply constraints and non-uniform
preference resolution.  It is notable that separations and recycle fuel
fabrication capacity are deployed identically in all simulations.  In the once
through case, the recycling loop never acquires material, and so reactors
always receive fresh \gls{UOX} fuel.  The \gls{DRE} ensures everything operates
smoothly in all cases.

### 2015-02-27 fundamentals/intro.tex
ORION isn't an acronym?
some edits

The cardinal purpose of a dyamic nuclear fuel cycle simulator is to calculate
the time- and facility-dependent mass flow through all or part the fuel cycle.
Dynamic nuclear fuel cycle analysis more realistically supports a range of
simulation goals than static analysis \cite{piet_dynamic_2011}. Historically,
dynamic nuclear fuel cycle simulators have calculated fuel cycle mass balances
and performance metrics derived from them using software ranging from ad hoc
spreadsheet-driven flow calculators to highly specialized system dynamics
modeling platforms. To date, current tools are often rigid rather than flexible,
fleet-based rather than discrete, or privately distributed rather than open
source. Each of these choices presents a challenge to modeling fidelity,
generality, efficiency, robustness, and scientific transparency.

@@

\Cyclus, is a dynamic, agent-based model, which employs a modular architecture,
an open development process, discrete agents, discrete time, and arbitrarily
detailed isotopic resolution of materials. Experience in the broader field of
systems analysis indicates that agent-based modeling enables more flexible
simulation control, without loss of generality
\cite{macal_agent-based_2010}. Furthermore, openness allows cross-institutional
collaboration, increases software robustness \cite{cohen_modern_2010}, and
cultivates an ecosystem of modeling and calculation options. This ecosystem is
comprised of flexible, interchangeable models of fuel cycle components with
varying scope, depth, and fidelity. It allows users and developers to customise
\Cyclus to analyze the cases that are of interest to them, rather than those the
simulator was originally developed to address.  The fundamental concepts of the
\Cyclus nuclear fuel cycle simulator capture these modern insights so that novel
challenges in nuclear fuel cycle analysis can be better addressed.

@@

Historically, domestic national laboratories have driven development and
regulated the use of their own tools:
\gls{VISION}\cite{jacobson_verifiable_2010},
\gls{DYMOND}\cite{yacout_modeling_2005}, and
\gls{NFCSim}\cite{schneider_nfcsim:_2005,allan_guidance_2008}.  Internationally,
other laboratories have created their own as well, such as
\gls{COSI}\cite{boucher_cosi_2005,boucher_cosi:_2006,meyer_new_2009,coquelet-pascal_comparison_2011}
and \gls{ORION}\cite{worrall_scenario_2007}.  Finally, some simulators initiated in a national lab setting have
been continued as propriety, industry-based simulators, such as
\gls{DANESS}\cite{van_den_durpel_daness_2009}.  Outside the national laboratories,
researchers have created new nuclear fuel cycle simulation tools when existing
tools were not available or not sufficiently general to calculate their metrics
of interest.  With limited access to the
national laboratory tools and a need to customize them for research purposes,
universities and private industry researchers have ``reinvented the wheel'' by
developing tools of their own from scratch and tailored to their own needs.
Examples include \gls{CAFCA}\cite{guerin_benchmark_2009} and
\gls{DESAE}\cite{andrianova_desae_2008,mccarthy_benchmark_2012,allan_guidance_2008}.

>>>>

The cardinal purpose of a dyamic nuclear fuel cycle simulator is to calculate
the time- and facility-dependent mass flow through all or part the fuel cycle.
Dynamic nuclear fuel cycle analysis more realistically supports a range of
simulation goals than static analysis \cite{piet_dynamic_2011}. Historically,
dynamic nuclear fuel cycle simulators have calculated fuel cycle mass balances
and performance metrics derived from them using software ranging from 
spreadsheet-driven flow calculators to highly specialized system dynamics
modeling platforms. To date, current tools are often rigid,
fleet-based, or privately distributed. Each of these choices presents a challenge to modeling fidelity,
generality, efficiency, robustness, and scientific transparency.

@@

\Cyclus, is a dynamic, agent-based model, which employs a modular architecture,
an open development process, discrete agents, discrete time, and arbitrarily
detailed isotopic resolution of materials. Experience in the broader field of
systems analysis indicates that agent-based modeling enables more flexible
simulation control, without loss of generality
\cite{macal_agent-based_2010}. Furthermore, openness allows cross-institutional
collaboration, increases software robustness \cite{cohen_modern_2010}, and
cultivates an ecosystem of modeling options. This ecosystem is
comprised of flexible, interchangeable models of fuel cycle components with
varying scope, depth, and fidelity. It allows users and developers to customise
\Cyclus to analyze the cases that are of interest to them, rather than those the
simulator was originally developed to address.  The fundamental concepts of the
\Cyclus nuclear fuel cycle simulator capture these modern insights so that novel
challenges in nuclear fuel cycle analysis can be better addressed.

@@

Historically, domestic national laboratories have driven development and
regulated the use of their own tools:
\gls{VISION}\cite{jacobson_verifiable_2010},
\gls{DYMOND}\cite{yacout_modeling_2005}, and
\gls{NFCSim}\cite{schneider_nfcsim:_2005,allan_guidance_2008}.  Internationally,
other laboratories have created their own as well, such as
\gls{COSI}\cite{boucher_cosi_2005,boucher_cosi:_2006,meyer_new_2009,coquelet-pascal_comparison_2011}
and ORION\cite{worrall_scenario_2007}.  Finally, some simulators initiated in a national lab setting have
been continued as propriety, industry-based simulators, such as
\gls{DANESS}\cite{van_den_durpel_daness_2009}.  Outside the national laboratories,
researchers have created new nuclear fuel cycle simulation tools when existing
tools were not available or not sufficiently general to calculate their metrics
of interest.  With limited access to the
national laboratory tools and a need to customize them for research purposes,
universities and private industry researchers have ``reinvented the wheel'' by
developing tools of their own from scratch and tailored to their own needs.
Examples include \gls{CAFCA}\cite{guerin_benchmark_2009} and
\gls{DESAE}\cite{andrianova_desae_2008,mccarthy_benchmark_2012,allan_guidance_2008}.
